%realize  LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{resume}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{url}
\usepackage{enumitem}
\setlength{\textheight}{10in} % increase text height to fit on 1-page

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tgbonum}


\begin{document}
\name{JINYANG YAO}

\basicInfo{
    \email{jinyangyaop@gmail.com} \textperiodcentered\
    \github{github.com/ailrk}  \textperiodcentered\
    \email{ailrk.github.io/home} \textperiodcentered\
    \linkedin[linkedin]{https://www.linkedin.com/in/jinyang-yao-649549208/} }


% \section{EDUCATION}
% The University of British Columbia, Kelowna, BC, Canada  \hspace{1.2in} \textbf{2017-Present}\\


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The University of British Columbia}, Kelowna, Canada}{2017 -- 2021}
\textit{B.S.} Honor in Compuster Science, Minor in Mathematics, Avg 86.9/100, GPA 3.95/4.33

\section{PAST EXPERIENCES}
    \datedsubsection{\textbf{Chongqing University HVAC department}}{2019 Summer}

    \itemnize
    \item Participated the ``Yangzi River area air conditioning and heating solution and its corresponding systems'' research project. Developed a program to select building designs that satisfies given multi-objective constraints.
     Designed and implemented the project's web platform with flask and react.

     \vspace{-0.1in}

    \datedsubsection{\textbf{UBC CS honor program}}{2020 - 2021}
        Using semi-supervised learning to assess programming assignments. Developed an iterative method allows human intervention to guide the algorithm to improve the clustering result.

     \vspace{-0.1in}

\section{PERSONAL PROJECTS}

    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf cppparsec } \>               \>\url{github.com/ailrk/cppparsec}\\
    \end{tabbing}

    \vspace{-0.3in}
    A C++ monadic parser combinator inspired by Haskell's parsec library.
    \vspace{-0.1in}

    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf pogger } \>               \>\url{github.com/ailrk/pogger}\\

    \end{tabbing}
    \vspace{-0.3in}
    A partially R5S5 compliant scheme implementation in Haskell.
    \vspace{-0.1in}

    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf lambda cube} \>               \>\url{github.com/ailrk/lambda-cube}\\

    \end{tabbing}

    \vspace{-0.3in}
    A set of langauges extended from the simply typed lambda calculus.
    \vspace{-0.1in}

    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf tml} \>               \>\url{github.com/ailrk/tml}\\
    \end{tabbing}

    \vspace{-0.3in}
    Template meta language. A ml style functional programming language in C++ template.
    \vspace{-0.1in}

    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf Blgol60 } \>               \>\url{github.com/ailrk/blgol60}\\

    \end{tabbing}
    \vspace{-0.3in}
    A haskell implementation of Algol60.
    \vspace{-0.1in}


\section{SKILLS}

    \textbf{Programming language :}
    Familiar with wide range of programming language.
    Most used: C++, Haskell, Python, Typescript Familiar: Ocaml, Rust, Commonlisp, Java.
    \\
    \vspace{-0.15in}

    \textbf{Compiler: }
    Familiar with DSL design including external DSL and embeded DSL with FOAS, HOAS, PHOAS.
    Familiar with program analysis process such as CFG analysis, Call graph analysis.
    Familiar with LLVM and LLVM IR.
    Familiar with various GC algorithms, parsing techniques and automatons theory.
    \\
    \vspace{-0.15in}

    \textbf{Programming language theory: } Understand operational, denotational, axiomatic semantics. Familiar with some abstract machines models such as SECD, Krivine, or Graph reduction.
    Familiar with languages in Lambda cube.
    Intuitionistic logic; Linear logic; Familiar with Agda and Lean.
    \\
    \vspace{-0.15in}

    \textbf{Platform: }  Familiar with system programming under linux. Familiar with GCC family tool chain, CMake.
    \\
    \vspace{-0.15in}

    \textbf{Web programming: } Flask; react; MySQL; sqlite lite; RESTFUL api designing. Understand SQLAlchemy and
    \\
    \vspace{-0.15in}

    \textbf{Language: }  English - Fluent, Mandarin - Native
    \\
    \vspace{-0.15in}

    \textbf{Others}:  Abstract Algebra and applications in error correction, Linear Programming,
    \\
    \vspace{-0.15in}

\end{document}
